%SketchEquations V1
\documentclass[10pt]{article}
\usepackage{times} 
\usepackage[margin=1.0in]{geometry}
\usepackage{layouts} %for adjusting layouts
\usepackage{mathtools}
%\usepackage[leqno]{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{xcolor,graphicx}
\usepackage{url}
\renewcommand{\UrlFont}{\normalsize}
\usepackage{verbatim}
\usepackage{makeidx}
\usepackage{float}

\usepackage[symbol*,stable]{footmisc}
\DefineFNsymbolsTM{myfnsymbols}{% def. from footmisc.sty "bringhurst" symbols
%  \textasteriskcentered *
  \textdagger    \dagger
  \textdaggerdbl \ddagger
  \textsection   \mathsection
  \textbardbl    \|%
  \textparagraph \mathparagraph
}%
\setfnsymbol{myfnsymbols}

\usepackage{abstract}
\usepackage[super]{natbib}

%http://texblog.org/2007/11/07/headerfooter-in-latex-with-fancyhdr/
\usepackage{fancyhdr}
\pagestyle{fancy}
%\fancyhead{}
\fancyfoot{}
\fancyfoot[C]{\thepage}
%\fancyfoot[L]{Yahoo! Confidential}
\renewcommand{\headrulewidth}{0.1pt}

% http://en.wikibooks.org/wiki/LaTeX/Hyperlinks
\usepackage{hyperref}
\hypersetup{ 
	colorlinks,
	urlcolor=blue,
	citecolor=blue,
	linkcolor=blue
}

%http://en.wikibooks.org/wiki/LaTeX/Document_Structure
\setcounter{tocdepth}{3}
\font\smalltt=cmtt10

\makeatletter
	\let\@copyrightspace\relax
\makeatother

\numberwithin{equation}{section}

\newenvironment{tighterdescription}%
  {\begin{description}%
    \setlength{\itemsep}{1pt}%
    \setlength{\parskip}{1pt}}%
  {\end{description}}

\newenvironment{tighterenumerate}%
  {\begin{enumerate}%
    \setlength{\itemsep}{1pt}%
    \setlength{\parskip}{1pt}}%
  {\end{enumerate}}

\newenvironment{tighteritemize}%
  {\begin{itemize}%
    \setlength{\itemsep}{1pt}%
    \setlength{\parskip}{1pt}}%
  {\end{itemize}}
  
\newcommand{\B}{\boldsymbol{\mathrm{B}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raggedbottom
\begin{document}
\title{Sketch Equations}
\author{Lee Rhodes \\
Yahoo! Inc., 701 First Ave., Sunnyvale, CA 94089, USA\\
}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{src/abstract.tex}
\input{src/introduction.tex}
\input{src/bernoulliEquations.tex}
\input{src/subsets.tex}
\newpage
\input{src/kmvEquations.tex}
%\input{src/equationDifferences.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\addcontentsline{toc}{chapter}{Bibliography}
\begin{thebibliography}{99}
%
\bibitem{BarYossef}
Z.~Bar-Yossef, T.~Jayram, R.~Kumar, D.~Sivakumar, and L.~Trevisan. 
Counting distinct elements in a data stream. 
{\em Randomization and Approximation Techniques In Computer Science}, 
pages 1–10. Springer, 2002.

\bibitem{Giroire2009}
F.~Giroire.
Order statistics and estimating cardinalities of massive data sets.
{\em Discrete Applied Mathematics}, 157-2:406--427, 2009.
%
\bibitem{Lang-2014}
Anirban Dasgupta, Kevin Lang, Lee Rhodes, Justin Thaler. A Framework for Estimating Stream Expression Cardinalities,
\href{http://datasketches.github.io/docs/ThetaSketchFramework.pdf}{Theta Sketch Framework}
%
\end{thebibliography}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\appendix
\input{src/evExample.tex}
\end{document}